Bullet Groups as a test of $\Lambda$CDM

### 2014-03-03 paper/ms.tex
article

We use the Bolshoi Run, a cosmological DM only simulation over a cubic
volume of 250 comoving \hMpc on a side. The simulation uses the ART code to
follow the evolution of  a dark matter density field sampled with
$2024^3$ from $z=80$ to $z=0$ [...]. The cosmology used  corresponds to  the spatially flat
concordance model with the following parameters:  the density
parameter for matter (dark matter$+$baryons) $\Omega_m=0.27$, the
density parameter for baryonic matter  $\Omega_b=0.0469$, the density
parameter for dark energy $\Omega_{\Lambda}=0.73$, the Hubble
parameter $h=0.7$, the 
normalization of the Power spectrum $n=0.95$ and the amplitude of mass
density fluctuation (at redshift z$=$0) $\sigma_8=0.82$.  The number
of particles used for each of the DM component was $2048^3$, resulting
in a mass resolution of $1.35 \times 10^8$ M$_{\odot}$h$^{-1}$.

\citet{2011ApJ...740..102K}.

@@

@@

We selected four snapshot of the simulation for four different
redshifts (z$=0$, z$=0.25$, z$=0.5$ and z$=1$) based in the
distribution of redshift in the Figure 1 by \citet{verdugo}, and  for
each sample in redshift we selected the host halo with circular
velocities greater than 300 kms$^{-1}$ and was split in two  principal
groups: The first group correspond to host halo with circular
velocities between 300 kms$^{-1}$ to 700 kms${^{-1}}$ with mass in the
range of $10^{12}$ M$_\odot{}$ to $10^{14}$ M$_\odot{}$ in the range
of mass of the Bullet Groups, and second group correspond to host halo
with circular velocities greater than 700 kms$^{-1}$ with mass
$\geq10^{14}$ M$_\odot{}$, in the range of mass of the Bullet
Clusters, in  the Table \ref{table1} is shown the two groups selected
in this work. For each group, we  classified the corresponding
substructures most massive and associated with the corresponding host
halo. The configuration of this system is shown in  Figure
\ref{configuration}, where you  an distinguish the host halo and
substructure for a particular configuration in z$=0$. In  this work,
we estimate the expected distribution of displacements
($d_{real,(X,Y)}$) in the projection 2-D that can estimate by
observations, these displacements correspond to the separation between
the minimal potential of the host halo and the  minimal potential of
the substructure, both are dark matter distributions.

\begin{table*}
\begin{center}
\begin{tabular}{ccccccc}\hline\hline
Sample       & Minimum Mass           & Maximum Mass          & \# Halos  & \# Halos  & \# Halos & \# Halos \\
             & M$_{\odot}$h$^{-1}$    & M$_{\odot}$h$^{-1}$   &   $z=0$   & $z=0.25$  & $z=0.5$  & $z=1$  \\\hline
Host Halo    & 0.35$\times{}10^{14}$  & 1.09$\times{}10^{14}$ &    400    &   362     &   310    &  192   \\
Substructure & 0.38$\times{}10^{11}$  & 0.30$\times{}10^{14}$ &    400    &   362     &   310    &  192   \\\hline
\end{tabular} 
\caption{Mass ranges for the two groups selected in this work in different redshifts.}
\label{table1}
\end{center}
\end{table*}

>>>>

We use the Bolshoi Run, a cosmological DM only simulation over a cubic
volume of 250 comoving \hMpc on a side. The simulation uses the ART code to
follow the evolution of  a dark matter density field sampled with
$2024^3$ from $z=80$ to $z=0$ [...]. The cosmology used  corresponds to  the spatially flat
concordance model with the following parameters:  the density
parameter for matter (dark matter$+$baryons) $\Omega_m=0.27$, the
density parameter for baryonic matter  $\Omega_b=0.0469$, the density
parameter for dark energy $\Omega_{\Lambda}=0.73$, the Hubble
parameter $h=0.7$, the 
normalization of the Power spectrum $n=0.95$ and the amplitude of mass
density fluctuation (at redshift z$=$0) $\sigma_8=0.82$.  The number
of particles used for each of the DM component was $2048^3$, resulting
in a mass resolution of $1.35 \times 10^8$ M$_{\odot}$h$^{-1}$. \citet{2011ApJ...740..102K}.

@@

The configuration of this system is shown in  Figure
\ref{configuration}, where can be distinguish the host halo and
substructure for the a particular configuration in z$=0$ and the 
mass ranges and number of host halos and substructures 
are summary in the Table \ref{table1}. Of all the possible configurations that can be presented
in Figure \ref{configuration}, we are interested in estimate in the simulation the number 
of Bullet Groups that may be present in an Universe of 250 $h^{-1}$Mpc. For this we selected 
of the simulations all the substructures  
whose velocities indicate a movement out of the host halo. Each halo in this sample has a quantity
called $X_{off}$ that corresponds to the distance halo center (the minimum of the gravitational potential) to 
the center of mass normalized by the
virial radius ($R_{vir}$). Values of $X_{off}$
equal to zero indicate relaxed halos, while $X_{off}>0$ indicates the existence
of perturbed halos which can be considered candidates to be Bullet Groups and this ditribution is shown 
in a scatter plot in the Figure \ref{cos_theta1} and the distribution of $\nu_{circ,Halo}/\nu_{circ,Sub}$ 
is shown in  Figure \ref{cos_theta2}, both figures for differents z.

\begin{table}
\begin{center}
\begin{tabular}{ccccccc}\hline\hline
Sample       & Minimum Mass           & Maximum Mass          & \# Halos  & \# Halos  & \# Halos & \# Halos \\
             & M$_{\odot}$h$^{-1}$    & M$_{\odot}$h$^{-1}$   &   $z=0$   & $z=0.25$  & $z=0.5$  & $z=1$  \\\hline
Host Halo    & 0.35$\times{}10^{14}$  & 1.09$\times{}10^{14}$ &    400    &   362     &   310    &  192   \\
Substructure & 0.38$\times{}10^{11}$  & 0.30$\times{}10^{14}$ &    400    &   362     &   310    &  192   \\\hline
\end{tabular} 
\caption{Mass ranges for the two groups selected in this work in different redshifts.}
\label{table1}
\end{center}
\end{table}

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_5_4.eps}
\end{center}
\caption{Scatter plot for $X_{off}$ as function of the relation between velocities of substructures and the host halos and 
for different z. The top panel is represented to the sample with $\nu>700$ kms$^{-}1$ and down panel is represented 
for $\nu<700$ kms$^{-1}$} 
\label{cos_theta1}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_5_2.eps}
\end{center}
\caption{Distributions of $\nu_{circ,Halo}/\nu_{circ,Sub}$ for differents z. The left panel correpond to the sample 
with $\v>700$ kms$^{-1}$ and right panel correpond to the sample with $\nu<700$ kms$^{-1}$.} 
\label{cos_theta2}
\end{figure*}

@@

We selected four snapshot of the simulation for four different
redshifts (z$=0$, z$=0.25$, z$=0.5$ and z$=1$) based in the
distribution of redshift in the Figure 1 by \citet{verdugo}, and  for
each sample in redshift we selected the host halo with circular
velocities greater than 300 kms$^{-1}$ and was split in two  principal
groups: The first group correspond to host halo with circular
velocities between 300 kms$^{-1}$ to 700 kms${^{-1}}$ with mass in the
range of $10^{12}$ M$_\odot{}$ to $10^{14}$ M$_\odot{}$ in the range
of mass of the Bullet Groups, and second group correspond to host halo
with circular velocities greater than 700 kms$^{-1}$ with mass
$\geq10^{14}$ M$_\odot{}$, in the range of mass of the Bullet
Clusters, in  the Table \ref{table1} is shown the two groups selected
in this work. For each group, we  classified the corresponding
substructures most massive and associated with the corresponding host
halo.  In  this work,
we estimate the expected distribution of displacements
($d_{real,(X,Y)}$) in the projection 2-D that can estimated by
observations, these displacements correspond to the separation between
the minimal potential of the host halo and the  minimal potential of
the substructure, both are dark matter distributions.
